Storm surge modelling in the Strait of Georgia

### 2014-07-24 RoughWork/manuscript.tex
A little bit more on intro paragraph

%some general intro paragraph here. Need something about SoG size, geography, islands, sills, rivers, tides....
The Strait of Georgia is a strongly stratified, semi-enclosed body of water located between Vancouver Island and the mainland of British Columbia. It is part of a larger system of waterways collectively known as the Salish Sea and is connected to the Pacific Ocean via the Strait of Juan de Fuca and Johnstone Strait.

@@

Communities in the Strait of Georgia are partiuclarly susceptible to storm surges in the winter months when there is an increased propensity for storms and a higher mean sea level caused by southeasterly winds and geostrophic adjustment \citep{danard2003storm}. In the summer months, the wind direction changes to northwesterly and mean sea level is lower. In British Columbia waters, the largest tidal range is typically observed in the winter months during the perigean spring tide or ``King" tide, when the sun and moon are aligned with the Earth and the moon is at its perigee. As such, storm surges are typically observed between Novemeber and Feburary. Several historical examples have been documented by \citet{forseth2006adaptation}. 
%work on this

%storm surge modelling

>>>>

%some general intro paragraph here. Need something about SoG size, geography, islands, sills, rivers, tides....
The Strait of Georgia is a strongly stratified, semi-enclosed body of water located between Vancouver Island and the mainland of British Columbia. It is part of a larger system of waterways collectively known as the Salish Sea and is connected to the Pacific Ocean via the Strait of Juan de Fuca and Johnstone Strait. It is on average 222 km in length and 28 km wide and its maximum depth is 420 m \citep{thomson1981oceanography}. At its southern end, the Strait of Georgia is connected to the Strait of Juan de Fuca through several passages, the largest being Haro Strait. The San Juan and Gulf Islands are scattered throughout these passages where complex bathymetry and steep topographic slopes induce vigorous tidal mixing. Many rivers feed fresh water into the Salish Sea system, the most siginificant source being from the Fraser River. Mixed diurnal and semi-diurnal tides are found throughout most of the Salish Sea but a semi-dirunal amphidrome is present nearby Victoria, where the tides are mainly diurnal. This system is home to several large coastal communities, such as Vancouver and Victoria, serves as a waterway for commericial traffic and recreational use, and supports a large and active fishing industry.

@@

Communities in the Strait of Georgia are partiuclarly susceptible to storm surges in the winter months when there is an increased propensity for storms and a higher mean sea level caused by southeasterly winds and geostrophic adjustment \citep{danard2003storm}. In the summer months, the wind direction changes to northwesterly and mean sea level is lower. In British Columbia waters, the largest tidal range is typically observed in the winter months during the perigean spring tide or ``King" tide, when the sun and moon are aligned with the Earth and the moon is at its perigee. As such, storm surges are typically observed between Novemeber and Feburary. Several historical examples have been documented by \citet{forseth2006adaptation}. 
%work on this
%something about fetch
%storm surge modelling
